Difference Scores: Paired Samples T-test

### 2024-03-07 examples/_1a_Examples_DifferenceScores_PairedTtests.qmd

::: blue
**This code reads in and shows the data to be used in the current
example**

>>>>

```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

# Authenticate with Google Drive
drive_auth()

:::

<!-- ::: blue
**This code reads in and shows the data to be used in the current
example** -->
